%====================
% EXPERIENCE A
%====================
\subsection{{Curricular Internship / AI Based Compilation for CGRA's \hfill Feb 2026 --- Present}}
\subtext{INESC TEC \hfill Porto, Portugal}
\begin{zitemize}
    \item Research position at \textbf{INESC TEC} on a project that is trying to advance the state of the art in the mapping problem for CGRA's.
    \item Researching and understanding how the state of the art is solving the mapping problem.
    \item Developing advancements with the use of \textbf{Graph Neural Networks} and \textbf{Deep-Q Learning} to solve the mapping problem.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Co-founder \& Full-stack Software Engineer \hfill Jan 2024 --- Jan 2026}}
\subtext{Ocean Informatix \hfill Porto, Portugal}
\begin{zitemize}
    \item Led end-to-end development of custom software and web solutions as the sole engineer, owning
architecture, implementation, deployment, and maintenance.
    \item Collaborated directly with clients to understand business needs, translate them into technical requirements, and
iterate quickly based on feedback.
    \item Designed and implemented solutions across multiple tech stacks, adapting to each client’s preferred frameworks,
environments, and constraints.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Alojamento Ideal \hfill Jun 2025 --- Sep 2025}}
\subtext{https://alojamentoideal.pt \hfill https://github.com/denizlg24/alojamentoideal}
\begin{zitemize}
    \item Designed and implemented a full-stack web app for property and activity booking and travel management
using \textbf{Next.js 15}.
    \item Implemented a dynamic booking system with real-time availability updates integrated with the \textbf{Hostify} property
management system, \textbf{Hostkit.pt} for invoicing and border control and \textbf{Bokun} for activities.
    \item Integrated payments with \textbf{Stripe} for secure payments and reliability.
    \item Deployed on \textbf{Vercel}, and using \textbf{MongoDB} for data storage.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Shortn.at \hfill Jun. 2023 --- Feb. 2024 (V1) May 2025 --- Jan 2026 (V2)}}
\subtext{https://shortn.at \hfill https://github.com/denizlg24/shortn\_v2}
\begin{zitemize}
    \item Shortn.at was my first full stack project. It started as a personal project but managed to retain some customers.
    \item As of Jan. 2026, I published V2 of Shortn and am now maintaining it and posting regular updates
    \item Version 2 was a complete rewrite of the project, due to a bigger volume of clients and new needs, and because
there were now many new technologies
    \item Version 2 is built on \textbf{Next.js 16}, with the new \textbf{React Compiler}. The database selection was kept although I
followed better principles thus increasing efficiency
    \item Version 2 had a full \textbf{CI/CD} pipeline with GitHub actions and is iterated using Agile Methodologies, with Sentry for
error monitoring.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{Envoy CLI \hfill Dec 2025 --- Feb 2025}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%    \item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%    \item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}

%====================
% EXPERIENCE F
%====================
%\subsection{{ROLE / PROJECT F \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company F \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE G
%====================
%\subsection{{ROLE / PROJECT G \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company G \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE H
%====================
%\subsection{{ROLE / PROJECT H \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company H \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE I
%====================
%\subsection{{ROLE / PROJECT I \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company I \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}